### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@e57ea9d4eb0871f6f3c329ab1b3c3e9c36e06456 🚀

\hypertarget{phylogeny-construction}{%
\subsection{Phylogeny Construction}\label{phylogeny-construction}}

@@

@@

@@

@@

\begin{figure}
\centering
\includegraphics{./figures/PR_ROC.png}
\caption{todo}
\end{figure}

>>>>

@@

\hypertarget{phylogeny-construction}{%
\paragraph{Phylogeny Construction}\label{phylogeny-construction}}

We construct phylogenies for both \emph{Bombus} and wildflower species
using barcode markers, mitochondrial COI and chloroplast rbcL,
respectively. These sequences were obtained from NCBI GenBank for all
species. For species for which no sequence was available (only a handful
of plants), their was substituted with a barcode from a member of the
same genus. Justify why this is fine here.

These sequences were aligned using ClustalOmega v???, and then a
posterior distribution of phylogenies and consensus tree was obtained
via MrBayes v??, using XX substition model with gamma-distributed rates.
Run until convergence, which here we define as the standard-deviation of
splits falling below 0.1.

\hypertarget{creating-an-embedding-from-phylogenies}{%
\paragraph{Creating an embedding from
phylogenies}\label{creating-an-embedding-from-phylogenies}}

We simulate traits.

@@

We take the 19 BioClim layers from CHELSA (cite; 1km resolution) and a
map of elevation and PCA them. A resulting 4 layers cover 99.5\% of the
variance. We use species occurrence data from GBIF, and consider each
occurrence record as a point in environment space. Then we fit a
multivariate normal distribution to these points in environmental space.

@@

We take the mean and variance of the distribution of number of
observations per week of year in the interaction field data.

@@

We fit a bunch of models using MLJ.jl.

Some of them are bagged, some are not bagged.

AUC-ROC and AUC-PR values below in fig.~\ref{fig:prroc}

\begin{figure}
\hypertarget{fig:prroc}{%
\centering
\includegraphics{./figures/PR_ROC.png}
\caption{todo}\label{fig:prroc}
}
\end{figure}
